Demo arXiv template

### 2022-10-10 paper/paper.qmd
more build on introduction

Indices quantify a concept of interest that is hard to measure using [...]. 
In finance and economic, the behavior of stock market, indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite uses a representative set of companies.
Natural hazard are also indices difficult to define because ....
Various drought, flood indices have been developed to characterise the severity and monitor from the perspective of meteorology, agricultural, hydrology, and also socio-economy. 
Examples of indices are ubiquitous: economic indices for quantifying productibility (GDP?), inflation (CPI), [...]; Social development indices like Human Development Index and Global Liveability Index; diversity indices to characterise the richness, evenness and dominance in ecology

Despite many measurements are called indices, they are actually not indices. 
A direct rate or transformation on a measured variable: birth & death rate computes the total number of new-borns and death per 1000 people. 
Many remote sensing measures are not indices, i.e. Normalized Difference Vegetation Index (NDVI), despite being named as an index, is a mere statistical transformation: the difference of near-infrared (NIR) and red visible channel over its sum.

@@

@@

  - domain scientists who propose new indices and [use multiple indices to compare]
  - decision makers, towards understand the 
  - statisticians, so as to [draw focus/ advocate] on statistical workflow

# Data pipeline in R

## Tidy data

@@

## Data pipeline

@@

A more recent data pipeline is tidymodels [@tidymodels], a set of packages for machine learning models following the tidyverse principles [@tidyverse]. \[expand on tidymodels\]

# A pipeline for building natural hazard indices

@@

# Incorporating new methods into the pipeline

@@

# Examples

>>>>

Indices quantify a concept of interest that is hard to measure using [...].
over time.
In finance and economic, the behavior of stock market, indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite uses a representative set of companies.
Natural hazard are also indices difficult to define because ....
Various drought, flood indices have been developed to characterise the severity and monitor from the perspective of meteorology, agricultural, hydrology, and also socio-economy. 
Examples of indices are ubiquitous: economic indices for quantifying productibility (GDP?), inflation (CPI), [...]; Social development indices like Human Development Index and Global Liveability Index; diversity indices to characterise the richness, evenness and dominance in ecology

Despite many measurements are called indices, they are actually not indices, but metrics. 
A direct rate or transformation on a measured variable: birth & death rate computes the total number of new-borns and death per 1000 people. 
Many remote sensing measures are not indices, i.e. Normalized Difference Vegetation Index (NDVI), despite being named as an index, is a mere statistical transformation: the difference of near-infrared (NIR) and red visible channel over its sum.

fire index

@@

There has not yet been a standardised workflow on index construction. 
For simple indices, users may be able to work out the calculation from the equations or workflow provided, while for more complicated construction, software is not even available for open-source consumption.
Even when the software implementation is available, most indices are computed through a single index command, for example, the package `SPEI` provides two drought indices: SPI and SPEI through function `spi()` and `spei()`. 
This software design focuses on the name of the index and includes all the steps in a single index function. 
With this design, there is little room for modification. For example, fit a new distribution that is not provided in the initial code. 
Also, when scaled to a large number of indices, it increases the cognitive load of remembering hundreds of index names. 
A better approach is to modularise these steps and construct a pipeline for users to build indices through choosing different building blocks from each module.
With this design, users focus on the operations involved in the index construction.
If an operation from another index is useful, users can borrow it to modify an existing index.

@@

The article contributes a pipeline framework to construct general indices.

  - domain scientists who propose new indices and directly use indices in analysis. [use multiple indices to compare]
  - decision makers, towards understand the 
  - statisticians, so as to [draw focus/ advocate] on statistical workflow and software design.

The rest of the paper is structured as follows: the concept of data pipeline in R is reviewed in @sec-data-pipeline-in-r.  @sec-a-pipeline-for-building-statistical-indices presents the data pipeline for index construction. @sec-incorporating-new-buliding-blocks-into-the-pipeline explains how to include a new building block in each pipeline module. 
Examples are given in @sec-examples to demonstrate the index construction with the pipeline built.

# Data pipeline in R {#sec-data-pipeline-in-r}

## Tidy data {#sec-tidy-data}

@@

## Data pipeline {#sec-data-pipeline}

@@

A more recent data pipeline is tidymodels [@tidymodels], a set of packages for machine learning models following the tidyverse principles [@tidyverse]. 
Steps: Exploratory data analysis (EDA), feature engineering, model tuning and selection, and model evaluation.

# A pipeline for building statistical indices {#sec-a-pipeline-for-building-statistical-indices}

@@

# Incorporating new buliding blocks into the pipeline {#sec-incorporating-new-buliding-blocks-into-the-pipeline}

@@

# Examples {#sec-examples}

### 2022-10-10 paper/paper.tex
more build on introduction

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, interior hidden, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Indices quantify a concept of interest that is hard to measure using
{[}\ldots{]}. In finance and economic, the behavior of stock market,
indices like Dow Jones Industrial Average, S\&P 500, and Nasdaq
Composite uses a representative set of companies. Natural hazard are
also indices difficult to define because \ldots. Various drought, flood
indices have been developed to characterise the severity and monitor
from the perspective of meteorology, agricultural, hydrology, and also
socio-economy. Examples of indices are ubiquitous: economic indices for
quantifying productibility (GDP?), inflation (CPI), {[}\ldots{]}; Social
development indices like Human Development Index and Global Liveability
Index; diversity indices to characterise the richness, evenness and
dominance in ecology

Despite many measurements are called indices, they are actually not
indices. A direct rate or transformation on a measured variable: birth
\& death rate computes the total number of new-borns and death per 1000
people. Many remote sensing measures are not indices, i.e.~Normalized
Difference Vegetation Index (NDVI), despite being named as an index, is
a mere statistical transformation: the difference of near-infrared (NIR)
and red visible channel over its sum.

@@

@@

\begin{itemize}
\tightlist
\item
  domain scientists who propose new indices and {[}use multiple indices
  to compare{]}
\item
  decision makers, towards understand the
\item
  statisticians, so as to {[}draw focus/ advocate{]} on statistical
  workflow
\end{itemize}

\hypertarget{data-pipeline-in-r}{%
\section{Data pipeline in R}\label{data-pipeline-in-r}}

\hypertarget{tidy-data}{%
\subsection{Tidy data}\label{tidy-data}}

@@

\hypertarget{data-pipeline}{%
\subsection{Data pipeline}\label{data-pipeline}}

@@

A more recent data pipeline is tidymodels (Kuhn and Wickham 2020), a set
of packages for machine learning models following the tidyverse
principles (Wickham et al. 2019). {[}expand on tidymodels{]}

\hypertarget{a-pipeline-for-building-natural-hazard-indices}{%
\section{A pipeline for building natural hazard
indices}\label{a-pipeline-for-building-natural-hazard-indices}}

@@

\hypertarget{incorporating-new-methods-into-the-pipeline}{%
\section{Incorporating new methods into the
pipeline}\label{incorporating-new-methods-into-the-pipeline}}

\hypertarget{examples}{%
\section{Examples}\label{examples}}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

Indices quantify a concept of interest that is hard to measure using
{[}\ldots{]}. over time. In finance and economic, the behavior of stock
market, indices like Dow Jones Industrial Average, S\&P 500, and Nasdaq
Composite uses a representative set of companies. Natural hazard are
also indices difficult to define because \ldots. Various drought, flood
indices have been developed to characterise the severity and monitor
from the perspective of meteorology, agricultural, hydrology, and also
socio-economy. Examples of indices are ubiquitous: economic indices for
quantifying productibility (GDP?), inflation (CPI), {[}\ldots{]}; Social
development indices like Human Development Index and Global Liveability
Index; diversity indices to characterise the richness, evenness and
dominance in ecology

Despite many measurements are called indices, they are actually not
indices, but metrics. A direct rate or transformation on a measured
variable: birth \& death rate computes the total number of new-borns and
death per 1000 people. Many remote sensing measures are not indices,
i.e.~Normalized Difference Vegetation Index (NDVI), despite being named
as an index, is a mere statistical transformation: the difference of
near-infrared (NIR) and red visible channel over its sum.

fire index

@@

There has not yet been a standardised workflow on index construction.
For simple indices, users may be able to work out the calculation from
the equations or workflow provided, while for more complicated
construction, software is not even available for open-source
consumption. Even when the software implementation is available, most
indices are computed through a single index command, for example, the
package \texttt{SPEI} provides two drought indices: SPI and SPEI through
function \texttt{spi()} and \texttt{spei()}. This software design
focuses on the name of the index and includes all the steps in a single
index function. With this design, there is little room for modification.
For example, fit a new distribution that is not provided in the initial
code. Also, when scaled to a large number of indices, it increases the
cognitive load of remembering hundreds of index names. A better approach
is to modularise these steps and construct a pipeline for users to build
indices through choosing different building blocks from each module.
With this design, users focus on the operations involved in the index
construction. If an operation from another index is useful, users can
borrow it to modify an existing index.

@@

The article contributes a pipeline framework to construct general
indices.

\begin{itemize}
\tightlist
\item
  domain scientists who propose new indices and directly use indices in
  analysis. {[}use multiple indices to compare{]}
\item
  decision makers, towards understand the
\item
  statisticians, so as to {[}draw focus/ advocate{]} on statistical
  workflow and software design.
\end{itemize}

The rest of the paper is structured as follows: the concept of data
pipeline in R is reviewed in Section~\ref{sec-data-pipeline-in-r}.
Section~\ref{sec-a-pipeline-for-building-statistical-indices} presents
the data pipeline for index construction.
Section~\ref{sec-incorporating-new-buliding-blocks-into-the-pipeline}
explains how to include a new building block in each pipeline module.
Examples are given in Section~\ref{sec-examples} to demonstrate the
index construction with the pipeline built.

\hypertarget{sec-data-pipeline-in-r}{%
\section{Data pipeline in R}\label{sec-data-pipeline-in-r}}

\hypertarget{sec-tidy-data}{%
\subsection{Tidy data}\label{sec-tidy-data}}

@@

\hypertarget{sec-data-pipeline}{%
\subsection{Data pipeline}\label{sec-data-pipeline}}

@@

A more recent data pipeline is tidymodels (Kuhn and Wickham 2020), a set
of packages for machine learning models following the tidyverse
principles (Wickham et al. 2019). Steps: Exploratory data analysis
(EDA), feature engineering, model tuning and selection, and model
evaluation.

\hypertarget{sec-a-pipeline-for-building-statistical-indices}{%
\section{A pipeline for building statistical
indices}\label{sec-a-pipeline-for-building-statistical-indices}}

@@

\hypertarget{sec-incorporating-new-buliding-blocks-into-the-pipeline}{%
\section{Incorporating new buliding blocks into the
pipeline}\label{sec-incorporating-new-buliding-blocks-into-the-pipeline}}

\hypertarget{sec-examples}{%
\section{Examples}\label{sec-examples}}
